A Survey of Range-Only SLAM Techniques and Sensors

### 2018-01-26 Paper.tex

	\includegraphics[width=90mm]{DNR.png}

@@

	\section{Beacon Initialization}
	Beacons initialization refers to the process by which beacons (or landmarks) at an unknown position receive their initial position estimation. One of the complications with RO-SLAM involves the issue of determining the location of landmarks when their initial placement is unknown, the EKF, which is used by many implementations, is especially sensitive to poorly initialized landmarks as they are used as the basis for the convergence of an accurate estimate. \cite{Caballero2010} presents a solution for this complication. A Gaussian Mixture Model is integrated into the EKF to create a multiple hypothesis filter.  This multiple hypothesis approach is used to solve the RO-SLAM problem and its use allows for the un-delayed initialization of landmarks, however a large number of hypothesis can lead to increased computational burden. \cite{Geneve2015} also puts forward a method that utilizes a Gaussian mixtures for beacon initialization in EKF, but in this method only two hypotheses and a Cartesian plane. \cite{Ahmad2011a} proposes to reduce the computational burden of methods, such as the one proposed by \cite{Caballero2010}, by introducing a novel state vector that eliminates the need for multiple hypothesis landmark representation. The paper proposes that under different circumstances the landmark could be represented using different parameters. Four circumstances are presented in the paper and the method is tested in simulation using both the EKF and a least squares optimization approach. The results showed that when the circumstances can be clearly distinguished between, an increase in performance is seen.

>>>>

	\includegraphics[width=90mm]{DNR.png}
%	\includegraphics[width=90mm]{DNR.png}

@@

	\section{Beacon Initialization}
	Beacons initialization refers to the process by which beacons (or landmarks) at an unknown position receive their initial position estimation. One of the complications with RO-SLAM involves the issue of determining the location of landmarks when their initial placement is unknown, the EKF, which is used by many implementations, is especially sensitive to poorly initialized landmarks as they are used as the basis for the convergence of an accurate estimate. \cite{Caballero2010} presents a solution for this complication. A Gaussian Mixture Model is integrated into the EKF to create a multiple hypothesis filter.  This multiple hypothesis approach is used to solve the RO-SLAM problem and its use allows for the un-delayed initialization of landmarks, however a large number of hypothesis can lead to increased computational burden. \cite{Geneve2015} also puts forward a method that utilizes a Gaussian mixtures for beacon initialization in EKF, but in this method only two hypotheses and a Cartesian plane. \cite{Ahmad2011a} proposes to reduce the computational burden of methods, such as the one proposed by \cite{Caballero2010}, by introducing a novel state vector that eliminates the need for multiple hypothesis landmark representation. The paper proposes that under different circumstances the landmark could be represented using different parameters. Four circumstances are presented in the paper and the method is tested in simulation using both the EKF and a least squares optimization approach. The results showed that when the circumstances can be clearly distinguished between, an increase in performance is seen.
	Beacons initialization refers to the process by which beacons (or landmarks) at an unknown position receive their initial position estimation. One of the complications with RO-SLAM involves the issue of determining the location of landmarks when their initial placement is unknown, the EKF, which is used by many implementations, is especially sensitive to poorly initialized landmarks as they are used as the basis for the convergence of an accurate estimate. Poorly approximated landmarks results in the divergence of the filter. These processes are furthur  divided into delayed and undelayed initializations.
	\subsection{Delayed initializations}
	These are the intialisations where  the robot intilaiialy moves around collects some measurements and initialises the location of the landmarks.This can be undersirable as it causes a delay in the localization of the robot where there is a immediate real time application. Localization can be performed only once a accurate estimations of the beacons are made. There are several methods that achieve this. 
	\subsubsection{Trilateration}
	[Pure Porbablisitc approach to SLAM] exmpalins a basic trilateration method where a basic 2D cicrcle intersectino technique. %more paperes needed
	\subsubsection{Particle filter}

	\cite{Caballero2010} presents a solution for this complication. A Gaussian Mixture Model is integrated into the EKF to create a multiple hypothesis filter.  This multiple hypothesis approach is used to solve the RO-SLAM problem and its use allows for the un-delayed initialization of landmarks, however a large number of hypothesis can lead to increased computational burden. \cite{Geneve2015} also puts forward a method that utilizes a Gaussian mixtures for beacon initialization in EKF, but in this method only two hypotheses and a Cartesian plane. \cite{Ahmad2011a} proposes to reduce the computational burden of methods, such as the one proposed by \cite{Caballero2010}, by introducing a novel state vector that eliminates the need for multiple hypothesis landmark representation. The paper proposes that under different circumstances the landmark could be represented using different parameters. Four circumstances are presented in the paper and the method is tested in simulation using both the EKF and a least squares optimization approach. The results showed that when the circumstances can be clearly distinguished between, an increase in performance is seen.
